Surface-driven registration method for the structure-informed segmentation of diffusion MR images\tnoteref{t1}

### 2015-11-11 Publications/2015-NeuroImage/06-discussion.tex
final fixes for resubmission

% -*- root: 00-main.tex -*-
\section{Discussion}
\label{sec:regseg-discussion}
\revcomment[C10 (R.2)]{%
We present \regseg{}, a simultaneous segmentation and registration method that
  maps a set of nested surfaces into a multivariate target-image.}
\revcomment[C1 (R.1)]{%
The nonlinear registration process evolves driven by the fitness of the
  picewise-smooth classification of voxels in the target volume imposed
  by the current mapping of the surfaces.}
\revcomment[moved]{%
We propose \regseg{} to map anatomical information extracted from \gls*{t1}
  images into the corresponding \gls*{dmri} of the same subject.
Previously, joint segmentation and registration has been applied successfully to
  other problems such as longitudinal object tracking \citep{paragios_level_2003}
  and atlas-based segmentation \citep{gorthi_active_2011}.
The most common approach involves optimizing a deformation model (registration)
  that supports the evolution of the active contours (segmentation),
  like \cite{paragios_level_2003,yezzi_variational_2003}.}
% Conversely, in structure-informed segmentation, the sources of variability are the geometrical distortions
%   after imaging and the anatomical evolution in longitudinal studies.}
\revcomment[C1 (R.1)]{%
\Regseg{} can be seen as a particular case of atlas-based segmentation-registration methods,
  replacing the atlas by the structural image of the subject (\emph{structure-informed segmentation}).}
\revcomment[C3 (R.1)]{%
The main difference of atlas-based segmentation and the application at hand is the resolution of the
  target image.
Atlas-based segmentation is typically applied on structural and high-resolution images.
A comprehensive review of joint segmentation and registration methods applied in atlas-based
  segmentation is found in \citep{gorthi_active_2011}.
They also propose a multiphase level-set function initialized from a labeled atlas to implement
  the active contours that drive the atlas registration.
Alternatively, \regseg{} implements the active contours with a hierarchical set of explicit
  surfaces (triangular meshes) instead of the multiphase level sets, and registration
  is driven by shape-gradients \citep{herbulot_segmentation_2006}.
As an advantage, the use of explicit surfaces enables segmenting \gls*{dmri} images
  with accuracy below pixel size.}

>>>>

% -*- root: 00-main.tex -*-
\section{Discussion}
\label{sec:regseg-discussion}
\revcomment[C10 (R.2)]{%
We present \regseg{}, a simultaneous segmentation and registration method that
  maps a set of nested surfaces into a multivariate target-image.}
\revcomment[C1 (R.1)]{%
The nonlinear registration process evolves driven by the fitness of the
  piecewise-smooth classification of voxels in the target volume imposed
  by the current mapping of the surfaces.}
\revcomment[moved]{%
We propose \regseg{} to map anatomical information extracted from \gls*{t1}
  images into the corresponding \gls*{dmri} of the same subject.
Previously, joint segmentation and registration has been applied successfully to
  other problems such as longitudinal object tracking \citep{paragios_level_2003}
  and atlas-based segmentation \citep{gorthi_active_2011}.
The most common approach involves optimizing a deformation model (registration)
  that supports the evolution of the active contours (segmentation),
  like \cite{paragios_level_2003,yezzi_variational_2003}.}
% Conversely, in structure-informed segmentation, the sources of variability are the geometrical distortions
%   after imaging and the anatomical evolution in longitudinal studies.}
\revcomment[C1 (R.1)]{%
\Regseg{} can be seen as a particular case of atlas-based segmentation-registration methods,
  replacing the atlas by the structural image of the subject (\emph{structure-informed segmentation}).}
\revcomment[C3 (R.1)]{%
The main difference of atlas-based segmentation and the application at hand is the resolution of the
  target image.
Atlas-based segmentation is typically applied on structural and high-resolution images.
A comprehensive review of joint segmentation and registration methods applied in atlas-based
  segmentation is found in \citep{gorthi_active_2011}.
They also propose a multiphase level-set function initialized from a labeled atlas to implement
  the active contours that drive the atlas registration.
Alternatively, \regseg{} implements the active contours with a hierarchical set of explicit
  surfaces (triangular meshes) instead of the multiphase level sets, and registration
  is driven by shape-gradients \citep{herbulot_segmentation_2006}.
As an advantage, the use of explicit surfaces enables segmenting \gls*{dmri} images
  with accuracy below pixel size.}
